% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

The acknowledgement listed below is just a sample for you to understand. Write appropriate acknowledgement w.r.t you seminar work. It is recomented not to use the same sentences listed below!...
I would like to thank my advisor, Dr. P Venkat Rangan for his tireless mentorship and support. I would also like to express my sincere gratitude to Prof. Unnikrishna Menon and Mr. Arun Balakrishann, the seminar coordinators  for their immense support and the time they dedicated to help me solving my doubts at various stages of the research.\\[1ex]
Thapasya\\
I am also indebted to Professors Maneesha V Ramesh,  and Balaji Hariharan for their research collaboration and their excellent teaching. I would also thank all faculty members of Amrita Center for Wireless Networks and Applications for their co-operation in completing this seminar. I also thank to my colleagues for the time they dedicated to discuss various research problems with me and for the spirit of camaraderie they helped foster in our laboratory.\\[1ex]

I would also like to express my gratitude for the immeasurable motivation and guidance provided by Sri. Mata Amritanandamayi Devi (AMMA), Chancellor of Amrita University. Above all, I thank God Almighty for his grace, for giving me strength and ideas for making this seminar work, flow smoothly.\\[1ex]

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
